Online Laterality Battery Pre-Processing - short version

### 2020-07-17 battery-preprocessing_v5_DB.Rmd
now removes data properly from "for_figs.csv"

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "https://osf.io/mhk29/download" #day 1 data

  if (d ==2){
    data_file <-  "https://osf.io/ebm6s/download"
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

@@

origdat<-finger.long
origdat$X1 <- origdat$`2`
mycolname<-"Day2_Finger_acc_Z"
polarity<- (1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)

@@

@@

        myrow <- myrow+1
        temp.dat$subject[myrow] <- z
        temp.dat$accurate[myrow] <- sum(tmp3$Correct,na.rm=TRUE) # add row for N accurate response
        temp.dat$trial[myrow] <- y
        temp.dat$side[myrow] <- if_else(s== 1, "Left", "Right")
      }
    }
  }
  chim.iter2<- temp.dat
  if (d==1)
  {chim.iter <- chim.iter2}
}
# now remove NAs to avoid any issues later
chim.iter <- na.omit(chim.iter)
chim.iter2 <- na.omit(chim.iter2)
# create another data frame
myrow.2 <- 0 # start row counter
CF.corrs <- data.frame(matrix(ncol = 2, nrow=200))
  colnames(CF.corrs) <- c("trial", "cor")
# LOOP THROUGH TRIAL SIZE
for (y in 2:trial) {
# task
task<-'Chimeric faces'  
# now identify the data frame
origdat <- chim.iter[chim.iter$trial== y,]
origdat$X1 <- origdat$accurate
mycolname<-"Day1_CF_moving"
mycutoff <- 0
polarity<- (-1)#so LI is positive in predicted direction
# select df
newsum <- dplyr::select(allsum, subject, exclude, lexTALE)
# make LIs for day 1
move <- makeLI(newsum,origdat,task,mycolname,polarity,mycutoff)
# make LIs for day 2
origdat2 <- chim.iter2[chim.iter2$trial== y,]
origdat2$X1 <- origdat2$accurate
mycolname<-"Day2_CF_moving"
move <- makeLI(move,origdat2,task,mycolname,polarity,mycutoff)
move <- move[move$exclude == 0 | move$exclude == 2,]
# correlate
move_corr <- cor(move[move$lexTALE <= 80,]$Day1_CF_moving, move[move$lexTALE <= 80,]$Day2_CF_moving, use= "complete.obs")

  # write to data 
  myrow.2 <- myrow.2+1
  CF.corrs$trial[myrow.2] <- y
  CF.corrs$cor[myrow.2] <- move_corr
}
# plot
CF.corrs <- na.omit(CF.corrs)
CF.cor.plot <- ggplot(CF.corrs, aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "blue") +
  geom_hline(yintercept=.75, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("B") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(CF.corrs[CF.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(CF.corrs[CF.corrs$cor >= .75,]$trial)))
}
```

Based on a couple of rounds with this, removing a lower limit on trials correct here is the only way to examine if less than 1 block would be enough to achieve r= .75. From this analysis, it appears that 27 trials would be sufficient to run the chimeric faces wirth reasonable reliability. Three repetitions of all combinations would lead to 48 trials (36 with different emotions in each hemifield, 12 same-same trials). This would ensure full balancing as 27 items would not allow an equal presentation of each of the four emotions across hemifaces.

@@

```{r reducerDL}
{for (d in 1:2){ #we will process day 1 and day 2 together
  dat <- dichotic_dat1
  if (d==2)
  {dat <- dichotic_dat2}

@@

        myrow <- myrow+1
        temp.dat$subject[myrow] <- z
        temp.dat$accurate[myrow] <- sum(tmp3$Correct,na.rm=TRUE) # add row for N accurate response
        temp.dat$trial[myrow] <- y
        temp.dat$side[myrow] <- if_else(s== 1, "Left", "Right")
      }
    }
  }
  dich.iter2<- temp.dat
  if (d==1)
  {dich.iter <- dich.iter2}
}
# now remove NAs to avoid any issues later
dich.iter <- na.omit(dich.iter)
dich.iter2 <- na.omit(dich.iter2)
# create another data frame
myrow.2 <- 0 # start row counter
DL.corrs <- data.frame(matrix(ncol = 2, nrow=400))
  colnames(DL.corrs) <- c("trial", "cor")
# LOOP THROUGH TRIAL SIZE
for (y in 2:trial) {
# task
task<-'Dichotic listening'  
# now identify the data frame
origdat <- dich.iter[dich.iter$trial== y,]
origdat$X1 <- origdat$accurate
mycolname<-"Day1_DL_moving"
mycutoff <- 0
polarity<- (-1)#so LI is positive in predicted direction
# select df
newsum <- dplyr::select(allsum, subject, exclude, lexTALE)
# make LIs for day 1
move <- makeLI(newsum,origdat,task,mycolname,polarity,mycutoff)
# make LIs for day 2
origdat2 <- dich.iter2[dich.iter2$trial== y,]
origdat2$X1 <- origdat2$accurate
mycolname<-"Day2_DL_moving"
move <- makeLI(move,origdat2,task,mycolname,polarity,mycutoff)
move <- move[move$exclude == 0 | move$exclude == 2,]
move <- move[move$lexTALE < 80,]
# correlate
move_corr <- cor(move$Day1_DL_moving, move$Day2_DL_moving, use= "complete.obs")

  # write to data 
  myrow.2 <- myrow.2+1
  DL.corrs$trial[myrow.2] <- y
  DL.corrs$cor[myrow.2] <- move_corr
}
# plot
DL.corrs <- na.omit(DL.corrs)
DL.cor.plot <- ggplot(DL.corrs, aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "blue") +
  geom_hline(yintercept=.75, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("A") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(DL.corrs[DL.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(DL.corrs[DL.corrs$cor >= .75,]$trial)))
}

>>>>

```{r readraw,include= FALSE, warning=FALSE}
# Set directory
for (d in 1:2){
  data_file <- "https://osf.io/mhk29/download" # day 1 data

  if (d ==2){
    data_file <-  "https://osf.io/ebm6s/download" # day 2 data
  }
  #we will assign raw data to all_dat2 (day2), but then reassign to all_dat1 on first run through loop, so we have correct data for each day
all_dat2 <- read.csv(data_file, na.strings = "NA",stringsAsFactors=F)
# cleaning - do operations that apply for all tasks
all_dat2 %>% filter(Attempt >= 1) # only answers 
# write as factors
all_dat2$subject <- as.factor(all_dat2$Participant.Public.ID)
all_dat2$RT <- as.numeric(as.character(all_dat2$Reaction.Time))
all_dat2$Trial <-as.numeric(all_dat2$Trial.Number) #useful if we want to restrict analysis to subset of trials so retain this variable
all_dat2$Task.Name <- as.factor(all_dat2$Task.Name)
all_dat2$word<-substring(all_dat2$word,66,(nchar(all_dat2$word)-4)) #remove format from written word stimuli
if (d==1)
{all_dat1 <- all_dat2}
}

@@

origdat<-finger.long
origdat$X1 <- origdat$`2`
mycolname<-"Day2_Finger_acc_Z"
polarity<- (-1)#so LI is positive in predicted direction
allsum <- makeZ(allsum,origdat,task,mycolname,polarity,mycutoff)

@@

# now calculate % correct
plot.data <- plot.data %>%
  mutate(remove= if_else(plot.data$task== "RD" & plot.data$p.corr < .75,1,
                         if_else(plot.data$accurate <= 10,1,0)))
plot.data <- plot.data[plot.data$remove== 0,]

@@

        myrow <- myrow+1
        temp.dat$subject[myrow] <- z
        temp.dat$accurate[myrow] <- sum(tmp3$Correct,na.rm=TRUE) # add row for N accurate response
        temp.dat$trial[myrow] <- y
        temp.dat$side[myrow] <- if_else(s== 1, "Left", "Right")
      }
    }
  }
  chim.iter2<- temp.dat
  if (d==1)
  {chim.iter <- chim.iter2}
}
# now remove NAs to avoid any issues later
chim.iter <- na.omit(chim.iter)
chim.iter2 <- na.omit(chim.iter2)
# create another data frame
myrow.2 <- 0 # start row counter
CF.corrs <- data.frame(matrix(ncol = 2, nrow=200))
  colnames(CF.corrs) <- c("trial", "cor")
# LOOP THROUGH TRIAL SIZE
for (y in 1:trial) {
# task
task<-'Chimeric faces'  
# now identify the data frame
origdat <- chim.iter[chim.iter$trial== y,]
origdat$X1 <- origdat$accurate
mycolname<-"Day1_CF_moving"
mycutoff <- 0
polarity<- (-1)#so LI is positive in predicted direction
# select df
newsum <- dplyr::select(allsum, subject, exclude, lexTALE)
# make LIs for day 1
move <- makeLI(newsum,origdat,task,mycolname,polarity,mycutoff)
# make LIs for day 2
origdat2 <- chim.iter2[chim.iter2$trial== y,]
origdat2$X1 <- origdat2$accurate
mycolname<-"Day2_CF_moving"
move <- makeLI(move,origdat2,task,mycolname,polarity,mycutoff)
move <- move[move$exclude == 0 | move$exclude == 2,]
# correlate
move_corr <- cor(move[move$lexTALE <= 80,]$Day1_CF_moving, move[move$lexTALE <= 80,]$Day2_CF_moving, use= "complete.obs")

  # write to data 
  myrow.2 <- myrow.2+1
  CF.corrs$trial[myrow.2] <- y
  CF.corrs$cor[myrow.2] <- move_corr
}
# plot
CF.corrs <- na.omit(CF.corrs)
CF.cor.plot <- ggplot(abs(CF.corrs), aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("B") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of chimeric faces required for at least .65 test-retest: ", min(CF.corrs[CF.corrs$cor >= .65,]$trial)))
print(paste0("Number of chimeric faces required for at least .75 test-retest: ", min(CF.corrs[CF.corrs$cor >= .75,]$trial)))
}
```

Based on a couple of rounds with this, removing a lower limit on trials correct here is the only way to examine if less than 1 block would be enough to achieve r= .75. From this analysis, it appears that 25 trials would be sufficient to run the chimeric faces wirth reasonable reliability. Three repetitions of all combinations would lead to 48 trials (36 with different emotions in each hemifield, 12 same-same trials). This would ensure full balancing as 25 items would not allow an equal presentation of each of the four emotions across hemifaces.

@@

```{r reducerDL}
for (d in 1:2){ #we will process day 1 and day 2 together
  dat <- dichotic_dat1
  if (d==2)
  {dat <- dichotic_dat2}

@@

        myrow <- myrow+1
        temp.dat$subject[myrow] <- z
        temp.dat$accurate[myrow] <- sum(tmp3$Correct,na.rm=TRUE) # add row for N accurate response
        temp.dat$trial[myrow] <- y
        temp.dat$side[myrow] <- if_else(s== 1, "Left", "Right")
      }
    }
  }
  dich.iter2<- temp.dat
  if (d==1)
  {dich.iter <- dich.iter2}
}
# now remove NAs to avoid any issues later
dich.iter <- na.omit(dich.iter)
dich.iter2 <- na.omit(dich.iter2)
# create another data frame
myrow.2 <- 0 # start row counter
DL.corrs <- data.frame(matrix(ncol = 2, nrow=400))
  colnames(DL.corrs) <- c("trial", "cor")
# LOOP THROUGH TRIAL SIZE
for (y in 1:trial) {
# task
task<-'Dichotic listening'  
# now identify the data frame
origdat <- dich.iter[dich.iter$trial== y,]
origdat$X1 <- origdat$accurate
mycolname<-"Day1_DL_moving"
mycutoff <- 0
polarity<- (-1)#so LI is positive in predicted direction
# select df
newsum <- dplyr::select(allsum, subject, exclude, lexTALE)
# make LIs for day 1
move <- makeLI(newsum,origdat,task,mycolname,polarity,mycutoff)
# make LIs for day 2
origdat2 <- dich.iter2[dich.iter2$trial== y,]
origdat2$X1 <- origdat2$accurate
mycolname<-"Day2_DL_moving"
move <- makeLI(move,origdat2,task,mycolname,polarity,mycutoff)
move <- move[move$exclude == 0 | move$exclude == 2,]
move <- move[move$lexTALE < 80,]
# correlate
move_corr <- cor(move$Day1_DL_moving, move$Day2_DL_moving, use= "complete.obs")

  # write to data 
  myrow.2 <- myrow.2+1
  DL.corrs$trial[myrow.2] <- y
  DL.corrs$cor[myrow.2] <- move_corr
}
# plot
DL.corrs <- na.omit(DL.corrs)
DL.cor.plot <- ggplot(abs(DL.corrs), aes(x=trial, y=cor)) +
  geom_hline(yintercept=.65, linetype="dashed", color = "red") +
  geom_line(size=1, alpha=0.8) + ylim(0, 1) + theme_classic() +
  xlab("No. of trials") + ylab("Test-retest reliability") + ggtitle("A") + theme(plot.title = element_text(hjust = 0.5))
# print number of trials needed
print(paste0("Number of dichotic required for at least .65 test-retest: ", min(DL.corrs[DL.corrs$cor >= .65,]$trial)))
print(paste0("Number of dichotic required for at least .75 test-retest: ", min(DL.corrs[DL.corrs$cor >= .75,]$trial)))
